---
title: "Visualisering af antal sagte ord 2"
output: html_notebook
author: baj
---
#Genbrug
Vi starter med alt det samme som i "visualisering-ord-sag.Rmd".
```{r, message=FALSE}
library(tidyverse)
library(here)
library(ndjson)
library(xslt)
library(fs)
library(ggplot2)
library(readxl)
library(tidytext)

require(readr)  # for read_csv()
require(purrr)  # for map(), reduce()

source(here("src/p017-functions.R"))
```
#Indlæs data
```{r}
here()
convert_TEI_to_JSONL(here("test-data"))
read_plays_jsonl(here("test-data")) -> plays
```
#Indlæs Excelarket
```{r}
variants <- read_excel(here("Rolleliste.xlsx")) %>% 
     unnest_tokens(variant, Alias, token = "regex", pattern = ", ") %>% 
    mutate(
      Karakter = tolower(Karakter),
      variant = tolower(variant)
    )
variants
```

## Indlæs stykkerne med fil-navne!
```{r}
# Alle stykker som json filer
json_file_list <- list.files(here("test-data"), pattern = "*.jsonl")
length(json_file_list)
head(json_file_list)

plays <- read_play_jsonl(here("test-data",json_file_list[1]))

for(i in 2:length(json_file_list)) {
  print(json_file_list[i])
  plays <- bind_rows(plays, read_play_jsonl(here("test-data",json_file_list[i])))
}

plays
```
#Sammenlæg navnevarianter
Husk at bruge Filnavn til noget!
```{r}
plays %>% mutate(speaker = tolower(speaker)) %>% 
  left_join(variants, by = c("filename"="Filnavn", "speaker"="variant")) %>% 
  mutate(speaker = if_else(!is.na(Karakter), Karakter, speaker)) %>%
  distinct -> plays
plays
```
Så langt, så godt.

# Nu tæller vi total antal ord sagt pr karakter pr stykke. Dernæst omregnet til procent af totale ord i stykket.
```{r}

# count words in "spoke"
(plays %>% 
  # remove rows that are not dialogue and empty speakers
  filter(!is.na(spoke), speaker != "") %>%
  
  # select only the columns, that we are interested in
  select(speaker, title, year, spoke) %>% 
  
  # add the number of spoken words
  mutate(n_spoken_words = str_count(spoke, '\\w+')) %>% 
  # remove the spoken words
  select(-spoke) %>%
  
  # group by title and speaker
  group_by(title, year, speaker) %>% 

  # Sum the words spoken by each speaker in each play
  # Lastly store the new data frame in a new reference for later use
  summarise(words = sum(n_spoken_words), title, year) %>%
    distinct() -> my_summary
)
   # Calculate %
(my_summary %>%
    ungroup(speaker) %>%
    summarise(words_play = sum(words)) -> totals)
   
(my_summary %>%
  full_join(totals) %>%
  summarise(freq = words / words_play, speaker, title, year, words, words_play) ->
    new_summary
    )
  # Sort by freq
(new_summary %>%
  arrange(desc(freq)))

```
Now "new_summary" holds all the information that we need. We sorted it to see who speaks the most. Next we choose a character to visualise...
In this example I choose "Jeronimus".

# Visualisering 
```{r}
character_plot <- function(character_name) {
  new_summary %>% 
  filter(speaker == character_name) %>%
  arrange(year) %>%
  ggplot(aes(fill = title, y = freq, x = title)) +
    geom_bar(stat="identity") +
    theme(legend.position="bottom") +
    labs(
      title = "Procent talte ord over år og komedier",
      subtitle = toupper(character_name),
      caption = "Kilde: DSL"
    ) +
  xlab("year") +
  ylab("Procent sagte ord") +
  facet_wrap(~year, ncol=nrow(new_summary), switch="x") +
  theme(axis.text.x=element_blank())
}

```

# Grafikker
## Henrik
```{r}
character_plot ("henrik")
ggsave("henrik_over_tid.pdf", width=18, height=9)
```
## Pernille
```{r}
character_plot("pernille")
ggsave("pernille_over_tid.pdf", width=16, height=9)

```

## Leander
```{r}
character_plot("leander")
ggsave("leander_over_tid.pdf", width=16, height=9)

```
## Leonora
```{r}
character_plot("leonora")
ggsave("leonora_over_tid.pdf", width=16, height=9)

```